\DailyTitle{6271 Log (October 4, 2010)}

\DailySection{Goals}

\begin{enumerate}
\item Make the hotline work!
\item Ecal spikes vs. hotline?
\item Read EXO-10-002-001 and compile a list of comments.
\item Bug Artur for DQM code
\item Bug Maurizio/Matthias for fitting strategy
\end{enumerate}

\DailySection{Summary List}

\begin{enumerate}
\item First attempt at running exotica hotline code.  Local running is fine.  For CAF access or to run cronjobs, I'll have to wait a bit.
\item Quickly read through EXO-10-002 and made a small list of comments.
\item Got the Hcal DQM instructions from Artur.
\item Start getting a signal shape sample.
\end{enumerate}

\DailySection{Making exotica hotline run as is}

Following instructions on the twiki \url{https://twiki.cern.ch/twiki/bin/viewauth/CMS/ExoticaHotline}.

\begin{enumerate}
\item First step is to run it locally and see if it works.
\begin{verbatim}
scramv1 project CMSSW CMSSW_3_8_2
cd CMSSW_3_8_2/src
cvs co -r V00-02-02 -d HotlineSkimCode/RecoSkim \\
   UserCode/ExoticaHotLine/src/HotlineSkimCode/RecoSkim
scramv1 build
cd HotlineSkimCode/RecoSkim/test
eval `scramv1 runtime -sh`
cmsRun hotlineSkim_AllFilters_cfg.py
\end{verbatim}
\item Successfully built.  \texttt{hotlineTopHadron\_cfi.py} is missing!  Copy from the checked out version from last week.
This example file read SUSY LM1 relval samples.
Now it seems to be working after copying the configuration file fragment.
\item Disk quota exceeded.  :(  Change to output to tmp directory.
\item Done.  The output is a edm format file with some events in it.  Meow.   \texttt{cmsShow} is cool.
\item Next thing to try is to setup cron job.
\begin{verbatim}
cd /afs/cern.ch/user/t/tulika/scratch2/ExoticaHotLine/cronJob
python exoHotLineCron.py Run2010B ExpressPhysics \\
   /afs/cern.ch/user/t/tulika/scratch2/ExoticaHotLine/CMSSW_3_8_2/src 
\end{verbatim}
\item Permission denied!!!  Oops.
\item Maria is asking Luca Malgeri for permissions on CAF.
\end{enumerate}

\DailySection{Reading of CMS paper draft EXO-10-002-001}

Information on the version read:
\begin{verbatim}
2010/09/21
Head Id: 17377
Archive Id: 17381
Archive Date: 2010/09/20
Archive Tag: trunk
\end{verbatim}

Overall it is a good paper, though it will be good to elaborate a bit on details.
Whether to add more detail to paper is another thing, but I would like to know how the analysis is done.
Main questions/comments below:

\begin{enumerate}
\item Line 26.  Why choose positive sign?
\item Line 54.  Cone size of 0.7 is huge, especially since the eta range is only 1.4 units or so for each region.
Is there any particular reason smaller cone sizes are not used?
\item Line 80-83.  Elaborate a bit more on this?  The reference didn't say much either.
\item Line 92.  How is the 20\% determined?
\item Figure 1.  The choice of division points for mass is perplexing....
\item Figure 1.  How much systematics is expected on pythia prediction?  Is it okay to plot the band too?
\item Line 100.  What is $\rho_j$ exactly?
\item Line 108-109.  Is the overall shift in units of ratio?  Could the choice of constant shift be justified?
\item Line 129-134.  Where does the 10x amplification come from?
\end{enumerate}

Cosmetics left for other people to pick.  I'm not good at English.

\DailySection{Hcal noise classification}

\begin{enumerate}
\item The most important thing is to get a sample of signal pulse shape, and also noises from a couple other runs.  Let me do that now.
\item Copied code from \texttt{Work} to \texttt{Workspace} on \texttt{lxplus}.  The code is in \\
\texttt{lxplus:scratch0/Workspace/HcalNoise/ExamplePulseShapes/6271}.  Batch submitted for signal pulses.
Input: DigiTree, Output: QM histograms and PulseShape tree.
\item The run time for individual job is about 20 minutes, as estimated by the test run.
\item Encountered ``No space left on device'' error.  Since the files are too large (more than 2 GB), so I copied them to local tmp folder before running....Orz....
\item For now, let's leave it there and see how bad it is.  All I need is some samples of pulses.
\item No.  Change it back to rfio access.  At least I will have some useful pulses this way.
\item Cloned a copy of the analyzer code to \\
\texttt{pccit28:Workspace/HcalNoise/PulseShapeVariableBrainStorm/6271}.
\item There are repeating entries due to castor error.  After 2GB is reached, trees won't be read and the content of the branches appear repeating.
\item For now make a comparison of ADC to previous entry, and if it is the same, drop the event.
\end{enumerate}

\DailySection{Checking status of the ZJets candle note}

\begin{enumerate}
\item First I need to find the svn repository....can't find it.
\item Maybe it's easier to bug people for it.
\end{enumerate}

\DailySection{Reflection}

Start from the afternoon, I was getting dizzy and lowered the work efficiency.  How can I improve this?

\DailySection{Goals for next work day}

\begin{enumerate}
\item Install DQM from Artur
\item Fit!
\item Finish up Hcal signal sample shape
\end{enumerate}


