\DailyTitle{6267 Log (October 3, 2010)}

\DailySection{Goals}

\begin{enumerate}
\item Understand the filtering logic behind exotica hotline
\item Make the hotline code work
\item Make a list of people to bug
\end{enumerate}

\DailySection{Summary List}

\begin{enumerate}
\item Read exotica hotline code and list the physics signatures it is catching.
\item Checked the event cleaning in exotica hotline.
\end{enumerate}

\DailySection{Reading exotica hotline code}

\DailySubSection{``Physics signature'' in exotica hotline}

Paths available in the \texttt{hotlineSkim\_AllFilters\_cfg.py}.
All paths are \texttt{basicFilters(NoPV) + ak5CaloJetsL2L3 + HBHENoiseFilter} and then
the target filter.

\begin{enumerate}
\item High Ht (\texttt{NoPV}).  \texttt{HtJetThreshold} = 30, \texttt{HtMin} = 700
\item High Met.  \texttt{PFMetMin} = 300
\item High Pt Electron.  \texttt{gsfElectron}, PT Min = 100
\item High Pt Photon.  150 GeV, \texttt{photons} collection
\item High Pt Jet.  350 GeV.  \texttt{ak5CaloJet}.
\item High Pt Muon.  80 GeV.  Standard muon collection.
\item Multi Track (\texttt{NoPV}).  600 tracks.  \texttt{generalTracks} collection
\item Multi Muon.  Two muons above 45 GeV.
\item Multi Electron (\texttt{NoPV}).  Two electrons above 45 GeV.
\item Multi Jet (\texttt{NoPV}).  Five jets above 50 GeV.
\item Multi Photon (\texttt{NoPV}).  Three photons above 30 GeV.
\item Top Electron (\texttt{NoPV}).  b-jet PT min 50 GeV, b-jet discriminator 1.7, one b-jet.
\texttt{HtJetThreshold} 30, \texttt{HtMin} 150.  At least one electrons above 80 GeV.
\item Top Muon (\texttt{NoPV}).  Same as the previous path.
\item Top Hadron (\texttt{NoPV}).  b-jet requirement same as before.  \texttt{HtMin} become 200.
\end{enumerate}

\DailySubSection{Event cleaning in exotica hotline}

\begin{enumerate}
\item Basic filters (with/without PV).
   \begin{enumerate}
   \item Primary vertex.  n.d.o.f. at least 4, max z deviation 25, max d0 deviation 2.
      \texttt{offlinePrimaryVertices} collection
   \item Physics declared.
   \item Scraping.  10 tracks above 0.2.
   \end{enumerate}
\item \texttt{ak5CaloJetL2L3}.  \texttt{JetMETCorrections.Configuration.DefaultJEC\_cff}.
\item \texttt{HBHENoiseFilter}.  Same as the one in \texttt{CommonTools.RecoAlgos.HBHENoiseFilter\_cfi}
except that the \texttt{EMF} requirement is added.  The version in \texttt{CMSSW\_3\_8\_2} is confirmed
to be the same as the ICHEP one.
\end{enumerate}

\DailySection{Reflection}

Orz.  Not much done today....  Sunday isn't really productive.

The ecal spike cleaning seems to be turned on by default before the hotline.  Maybe we want to somehow read from
the uncleaned version of it, and coincide spike signature with physics signature.  But for the time being I'll reverse
the Hcal filter only.


\DailySection{Goals for next work day}

\begin{enumerate}
\item Make the hotline work!
\item Ecal spikes vs. hotline?
\item Read EXO-10-002-001 and compile a list of comments.
\item Bug Artur for DQM code
\item Bug Maurizio/Matthias for fitting strategy
\end{enumerate}


