\DailyTitle{6334 Log (October 28, 2010)}

\DailySection{Goals}

\begin{enumerate}
\item R\&D on double-chi2 tree.
\item With muon veto, look at remaining noise.
\end{enumerate}

\DailySection{Summary List}

\begin{enumerate}
\item Added muon counts to the tree
\item Tested the idea of adding a off-time penalty to the nominal chi2 fitting
\item Checked late valid-looking pulse.
\end{enumerate}

\DailySection{Testing out modified $\chi^2$ - adding timing and fit parameter information}

\DailySubSection{Adding timing offset from the nominal fit}

From the offset distribution of signal (\texttt{Jet} dataset, 100 fC threshold), the peak is at offset -109.
Therefore we can add an additional term to penalize the nominal fit from going too far.  The modified $\chi^2$ is

\begin{equation}
\chi^2 = \left(\sum_{i=1}^{10} \left(\dfrac{F(i) - TS_i}{\sigma_{TS_i}}\right)^2 \right)
   e^{+\dfrac{(t-<t>)^2}{2 \sigma^2}},
\nonumber
\end{equation}

where $F(i)$ is the ideal pulse, $TS_i$ is the pulse, and $t$ the offset, $<t>$ average (expected) offset.
When the width is set to 25 ns, no too much has changed in both signal and noise.  Noise sample
moves more to the negative $\Lambda_{linear}'$ side than signal.
Still not usable.
Try to rerun with 12.5 ns.  The noise sample moves even more....but it seems that they approach $\Lambda_{linear}' = 0$.
Same story as before, let's try to look at them and see if we can design anything new for them.

\DailySubSection{Pulses where $\Lambda_{linear}' - \Lambda_{linear} > 1$}

They all share the same characteristic.  Most of them are good-looking pulses, but one TS late.
Not sure what is causing this.  If the tracking looked only in TS4, then it's normal that there isn't a PV around.
In that case something probably pre-fired.  Let's look at a few event display.

....No, usually there isn't much around in these events.  What is going on?

\DailySection{Reflection}

\DailySection{Goals for next work day}

