\DailyTitle{6325 Log (October 22, 2010)}

\DailySection{Goals}

\begin{enumerate}
\item Put codes from Shuichi's student and also the Jason variable and pulse shape fitting in Hcal DQM.
\item Check Matthias' note and see what I need to put in.
\item Make a plan of rerunning Hcal digi trees and include some more information.
\end{enumerate}

\DailySection{Summary List}

\begin{enumerate}
\item Implemented the test variables (and Jason's TS4TS5 variable) into offline DQM testbench.
\item Putting part of Shuichi et al.'s code into the DQM testbench.
\item Added an ad-hoc version of JP's isolation filter into the DQM testbench.  Everything becomes so slow....
\end{enumerate}

\DailySection{Check code from Shuichi et al}

Starting from \texttt{HcalNoiseMon/NoiseAnalyzer/src/HcalNoiseInfoAnalyzer.cc}.
Clean collision events if any of these are satified:

\begin{enumerate}
\item IC5 calo jet.  Reject if any jet with 8 GeV/c, $|\eta| < 2.95$, EM fraction \textgreater 0.05
\item Any track (from the \texttt{generalTracks} collection) above 0.1 GeV/c
\end{enumerate}

Get CaloMET collection, L1 trigger and fill some histogram. Loop over \texttt{HcalNoiseRBXCollection} collection.
Consider a certain RBX only if number of rechits \textgreater 0 and the total energy \textgreater 10 GeV
(threshold 1.5 GeV).  Consider HPD only if there is one hit above 5 GeV.
Noise category:

\begin{enumerate}
\item Category 1 (RBX): MaxHPD/RBX $\le 0.98$, E2/E10 $> 0.8$, RBX hit $= 10$.  (bug!?)
\item Category 2 (RBX): MaxHPD/RBX $\le 0.98$, E2/E10 $< 0.33$.
\item Category 3 (RBX): MaxHPD/RBX $\le 0.98$, $0.33 \le $ E2/E10 $< 0.8$.
\item Category 4 (RBX): MaxHPD/RBX $\le 0.98$, E2/E10 $> 0.8$, RBX hit $> 10$.
\item Category 5 (RBX): MaxHPD/RBX $\le 0.98$, E2/E10 $> 0.8$, RBX hit $< 10$.
\item Category 6: undefined.
\item Category 7 (HPD, HPD discharge): MaxHPD/RBX $> 0.98$, nHitsHighest (in highest HPD) $\ge$ 9.
\item Category 8 (HPD, HPD ion feedback): MaxHPD/RBX $> 0.98$, nHitsHighest (in highest HPD) $<$ 9.
\end{enumerate}

Then it's a lot of histogram filling.
There are literally a few hundred histograms.  What should I put in?
Let's choose a few to start with

\begin{enumerate}
\item Max zero, total zero, E2/E10 trio, HPD/RBX hit count
\item Hcal noise category summary plot (count of each type of noise, with respect to RBX)
\end{enumerate}

\DailySection{Notes on Hcal DQM implementation}

It's possible to have sub-directories.  We do not need to declare the directories beforehand.
The only thing to do is to set the subdirectory before booking histograms.  They will be automatically created.

\DailySection{Reflection}

\DailySection{Goals for next work day}

\begin{enumerate}
\item Eat lunch
\item Eat dinner
\item Find the red herring
\end{enumerate}


