\DailyTitle{6264 Log (Septemper 30, 2010)}

\DailySection{Goals}

\begin{enumerate}
\item Go through vecbos meetings in september
\item Go through Hcal meetings in september
\item Move the logbook to subversion
\item Make a list of things to do for the candle note
\end{enumerate}

\DailySection{Summary List}

\begin{enumerate}
\item Skimmed through vecbos meetings in espace and V+Jet meetings
\end{enumerate}

\DailySection{Go through vecbos meetings in September}

\DailySubSection{Espace meetings}

\begin{enumerate}
\item September 8, "Thresholds" by Maria Spiropulu.   Default value: CaloJet 30, UncorrectedCalo 20, Track 15, PF 30
\item September 8, "Lucas Fit" by Lukas Vanelderen.
   \begin{enumerate}
   \item Fit MT for W, t+X, other
   \item Fix shape to MC for W, t+X, and float the other
   \item "W and top+X separated well and unbiassed from other"
   \item Fit W+LF vs. W+HF with t+X, and use the HF fraction from MC to recover W yield
   \end{enumerate}
\item September 15, "btag" by Lukas Vanelderen.  Control sample for HF from data.  Need to read about b-tagging algorithms.
\item September 15, "Vecbos Meeting" by Matthias Ulrich Mozer.  Revisit uncertainties on AlphaL and AlphaR.
   \begin{enumerate}
   \item Traditional fit: fix alpha to best known value, and redo fit with different alpha to get uncertainty
   \item Nuisance parameter: constrain alpha by a gaussian centered at the best known value.
   \item 7-fit plot.
   \end{enumerate}
\item September 22, "Vecbos Meeting".  "W and Z + jets" by E. di Marco in General EWK meeting.
\item September 22, "Vecbos Meeting".  Lukas updated results on WJet fit.
\item September 22, "Vecbos Meeting".  Will Reece updated on trigger efficiencies.
\item September 29, "W fit strategy, flavor part" by Lukas Vanelderen.
Estimate PDF from b-tag variables from control samples for t+X and W+LF.  Seems to have problem in the 2Jet bin.
\end{enumerate}

\DailySubSection{V+Jet meetings}

\begin{enumerate}
\item September 7.  Lukas on fit strategy in W+Jets (sane as the one in espace).  Z candle analysis status report (with toys).
\item September 21, "Introduction on Zbb issues and current plans" by Alexandre Nikitenko.  Z+b is similar to H+b
\item September 21, "Task list overview" by Vitaliano Ciulli and Ilaria Segoni.
\item September 28, "Report on Zbb analysis" by Anne-Marie Magnan.
\item September 28, "Report on Zb(b) analysis" by Natalie Heracleous.
\item September 28, "Update on Z(ee)+jets and W(enu) +jet studies" by Sarah Malik. (....)
\item September 28, "Status on PFlow Z+Jets Analysis" by Anil Pratap Singh.
\end{enumerate}

\DailySection{Reflection}

\DailySection{Goals for next work day}

% \begin{enumerate}
% \item Meow.
% \end{enumerate}


