\DailyTitle{6322 Log (October 19, 2010)}

\DailySection{Goals}

\begin{enumerate}
\item Z candle MC plots - recreate all plots and tables (and identify things that are missing)
\item Implement Shuichi's code into the DQM structure
\item Make the digi tree/pulse shape tree of those picked events
\item Finish up Hcal noise presentation.  Add a couple slides on parabolic fit.
\item Finish up vecbos jobs
\item Investigate what the small group of pulses are in signal events where linear fit is better
\item Lower priority: Introduce double-chi2 variables into Hcal DQM structure
\end{enumerate}

\DailySection{Summary List}

\begin{enumerate}
\item Finished up Hcal noise presentation draft.  Sent to Maria and Artur for comments.
\item Made a skim of the 35 events from last Friday.
\item Code from Shuichi's student is only available inside FNAL.  :(
\item Investigated the small group of pulses in the linear test variable.
\end{enumerate}

\DailySection{Comments on the hcal noise presentation}

\begin{enumerate}
\item Check if the chi2 distribution looks like chi2
\item Try to make the RMS8/Max into a fit.
\item Event selection.  Use other parts of detector to make sure there is less signal contamination.
\item Give the test variables names.
\end{enumerate}

\DailySection{The small group of pulses in the signal population where linear test variable is negative}

All of them look like noise.  There is no peak anywhere in the 10 time slices.  I haven't looked at the geometrical distribution,
but it should be pretty safe to cut out.

\DailySection{Reflection}

???

\DailySection{Goals for next work day}

\begin{enumerate}
\item Create MC plots for Z candle
\item Submit MultiJet jobs
\item Try out low-N fit
\end{enumerate}


