\DailyTitle{6474 Log (January 13, 2011)}

\DailySection{Summary List until now}

\DailySubSection{Vecbos - V+Jet rush}

\begin{enumerate}
\item Helped out with fitting in the PF-based ratio muon analysis: both constrained and unconstrained fits, 15/30 GeV.
\item Helped out with producing double-ratio plot for comparison between W and Z
\item Written a short overview in the new note for the above two items.
\item Made a toy study to extract pulls of alpha and beta given current data statistics.
\item Upgraded the unconstrained fit to include the 0-jet bin also.  Shape is different in that bin.
\end{enumerate}

\DailySubSection{Vecbos - Moving on}

Had a meeting with Maurizio and Matthias on 6473.  Rough roadmap for moving on:

\begin{enumerate}
\item On January 20 there is a SUSY meeting, and February 15 is the final cutoff (or so it was rumored) for any pre-approval using 2010 data.
\item The plan is to first see if we can say anything by comparing the 4-jet bin in data vs. prediction from the first 3 bins.
\item If we're fast, we can do a model-dependent search by plugging in PDF from MC in various SUSY points and see if anything can be said.
\item If we're really fast, we can try something with some simplified model (will be provided by Joe?)....that's for later.
\item There is also the side-study of making s-plots to get number of b-tagged jets in signal events.  This is important for Hbb group and shouldn't be too hard.
\end{enumerate}

\DailySubSection{Hcal noise}

\begin{enumerate}
\item Code going in to CMSSW version 3-11.
\item An effort has started to characterize the temporal characteristics of each subtypes of noise.
\item Started Looking at run evolution and lumi evolution vs. RBX for different kinds of noise...
\item Started dijet fake rate studies
\end{enumerate}

\DailySubsection{Others}

\begin{enumerate}
\item Read through HI jet quenching note.
\end{enumerate}


