\DailyTitle{6273 Log (October 6, 2010)}

\DailySection{Goals}

\begin{enumerate}
\item Read and understand the double spike algorithm
\item Make sure if anyone is doing the vecbos PDMu dataset
\item Make a set of loose cuts to remove obvious noise, and skim through pulse shapes of the rest
\item Port the HCAL ideal pulse shape (as in \texttt{CMSSW}) to \texttt{RooFit}
\item Vecbos fitting strategy?
\item To-do chart for ZJets candle note for fast execution once target data ($\sim 50 pb^{-1}$) arrives
\end{enumerate}

\DailySection{Summary List}

\begin{enumerate}
\item Made a checklist and sent to Maurizio for comment
\end{enumerate}

\DailySection{Vecbos to-do chart}

\begin{enumerate}
\item Data, numbers after each cut.  (Ready)
\item Data, tight isolation to get alphaL.  (Ready)
\item Data, simultaneous fit to get the right error on signal inclusive
yields without enforcing linear constraint.  (Ready)
\item Data, fit with the linear constraint.  To be compared with the one
without enforcing constraint.  (Coming soon)
\item Data, get the ratio plot from the result of the fit.  (Need the
script to take the fit output and make the final plot)
\item Data, repeat the fit 4 times for JEC uncertainty.  (Not yet
done...coming soon)
\item Data, anti-isolation selection.  (Ready)
\item Data, splot to get Z PT, leading-jet PT spectrum, etc. (???)
\item MC, numbers after each cut, as well as numbers in each jet bin.  (Ready)
\item MC, demonstration that the isolation does not have a large impact on
alphaL.  (Ready)
\item MC, anti-muon selection \& QCD normal selection.  (Ready...though QCD
sample is small)
\item MC, justify that an isolation is needed with PF stuff.  (Ready)
\item MC, $Z \rightarrow \mu\mu$ PT shape vs. $Z \rightarrow \nu\nu$ MET shape comparison.  (Not yet done)
\item MC, efficiencies in different jet bin.  (Not ready)
\item Toy MC, on the functional form itself.  Generate sample with
cruijff, fit to check the spread.  (OK, repeatable within a day)
\item Toy MC, if the parameters are off, how much bias will there be.
Show that only alphaL matters.  (OK, repeatable within a day)
\item Show that the error we get from the simultaneous fit is reasonable (???)
\item Efficiency of the trigger (???)
\end{enumerate}

Reply from him:

\begin{enumerate}
\item There is a tool to calculate splots in \texttt{RooStat}
\item Not much to be done in trigger efficiency
\end{enumerate}

\DailySection{Reflection}

An extremely slow day....

\DailySection{Goals for next work day}

\begin{enumerate}
\item Read and understand the double spike algorithm
\item Make sure if anyone is doing the vecbos PDMu dataset
\item Make a set of loose cuts to remove obvious noise, and skim through pulse shapes of the rest
\item Port the HCAL ideal pulse shape (as in \texttt{CMSSW}) to \texttt{RooFit}
\end{enumerate}


