\DailyTitle{7722 Log (April 10, 2012)}

\DailySection{Plan for today (and onwards)}

The main goal for today is to rush in the background estimation from photon+jet.

\begin{enumerate}
\item Look at photon-related variables for different samples.
While I don't have easy MC access, hopefully we can verify that the cuts
(standard ones at least) makes sense.  What to do with isolation?
\item Rerun everything treating first photon as invisible, and maybe reject events
with too many photon candidates.   Look at razor distributions.
\item Derive correction factor from data with Zmumu
\item Apply everything and compare with Znunu MC - check that inclusive works
\item Apply everything with b-jets, and derive shape.
\end{enumerate}


\DailySection{Checking photon id variables}

From the samples done in the past few days, I looked at the photon ID variables.
Distributions of the variables look roughly fine, but some distributions look weird.
For example H/E distribution, when split into photons with pixel seed and without.
The distribution with pixel seed drops faster at low values, and flattens out faster,
while ones without pixel seed drops slower.  Above H/E 0.15 curve with pixel seed
vanishes, and there's a jump up in the no-seed distribution.  Then above 0.5 it
jumps down again.  In the QCD sample there is a population at very low H/E value,
while photon+jet sample it's more smooth falling.

The photon ID used in SUSY diphoton+MET analysis is listed here for reference.
In their trigger, they have the "IsoVL" version of photon isolation

\begin{enumerate}
\item Ecal $E_T$ within $\Delta R 0.3 < 0.012 \times E_T + 6$ GeV
\item Hcal $E_T$ within $\Delta R 0.3 < 0.005 \times E_T + 4$ GeV
\item Tracker $P_T$ within $\Delta R 0.3 < 0.002 \times E_T + 4$ GeV
\item $R9 > 0.8$
\end{enumerate}

During offline analysis,

\begin{enumerate}
\item $|\eta| < 1.4442$
\item $P_T > 40 (25)$ for the first two photons
\item Combined isolation (rho-corrected) $<$ 6 GeV
\item $H/E < 0.05$
\item $\sigma_{i\eta i\eta} < 0.011$
\item $R9 < 1.0$
\end{enumerate}





